NumPy---Array Programming in Python

### 2020-02-07 body.tex
Minor edits / feedback from Tyler

Many research groups have designed large,
complex scientific libraries, which add specialized functionality for
solving problems in specific domains.
For example, the \code{eht-imaging} library developed by the Event Horizon Telescope 
collaboration for radio interferometry imaging, analysis, and simulation
relies on many components of the scientific Python ecosystem.
NumPy arrays are used to store and manipulate numerical data at every step
in the processing chain: from raw data through calibration and image
reconstruction.
SciPy is used to provide tools used in general image processing such as
filtering and image alignment, while scikit-image, an image processing
library that extends SciPy, provides higher-level functionality such as
edge filters and Hough transforms.
Other components of SciPy are used throughout the library, such as the
\code{scipy.optimize} module for handling mathematical optimization tasks.
NetworkX \cite{SciPyProceedings_11}, a package for complex
network analysis, is used for the analysis of consistency among image
comparisons.
The community-developed astronomy library, Astropy \cite{astropy:2013, astropy:2018},
is used throughout \code{eht-imaging}, primarily to handle standard
astronomical file formats and time/coordinate transformations.
Matplotlib is used for visualizing data throughout the analysis pipeline,
including for the generation of the final image of the black hole.

>>>>

Many research groups have designed large,
complex scientific libraries, which add specialized functionality for
solving problems in specific domains.
For example, the \code{eht-imaging} library \cite{chael2019ehtim} developed by the Event Horizon Telescope 
collaboration for radio interferometry imaging, analysis, and simulation
relies on many components of the scientific Python ecosystem.
NumPy arrays are used to store and manipulate numerical data at every step
in the processing chain: from raw data through calibration and image
reconstruction.
SciPy is used to provide tools used in general image processing such as
filtering and image alignment, while scikit-image, an image processing
library that extends SciPy, provides higher-level functionality such as
edge filters and Hough transforms.
Other components of SciPy are used throughout the library, such as the
\code{scipy.optimize} module for handling mathematical optimization tasks.
NetworkX \cite{SciPyProceedings_11}, a package for complex
network analysis, is used for the analysis of consistency among image
comparisons.
The community-developed astronomy library, Astropy \cite{astropy:2013, astropy:2018},
is used throughout \code{eht-imaging}, primarily to handle standard
astronomical file formats and time/coordinate transformations.
Matplotlib is used for visualizing data throughout the analysis pipeline,
including for the generation of the final image of the black hole.

### 2020-02-07 methods.tex
Fix spelling of PyData/Sparse.
Minor edits / feedback from Tyler

NumPy plays a central role in building and standardizing much of the scientific
Python community infrastructure.
The docstring standard mentioned in the history section is now widely adopted.
We are also now using the NEP system as a way to help coordinate the larger
scientific Python community.
% https://numpy.org/neps/nep-0029-deprecation_policy.html
For example, in NEP 29, we recommend, along with leaders from various other
projects, that all projects across the Scientific Python ecosystem adopt a
common ``time window-based'' policy for support of Python and NumPy versions.
This standard will simplify downstream project and release planning.

@@

A vast number of projects are built on NumPy;
these projects are consumers of the NumPy API.
Over the last several years, a growing number of projects are providers of
a \emph{NumPy-like API} and array objects targeting audiences with specialized
needs beyond NumPy's capabilities.
For example, the NumPy API is implemented by several popular tensor computation
libraries including CuPy\footnote{\url{https://cupy.chainer.org/}},
JAX\footnote{\url{https://jax.readthedocs.io/en/latest/jax.numpy.html}},
and Apache MXNet\footnote{\url{https://numpy.mxnet.io/}}.
PyTorch\footnote{\url{https://pytorch.org/tutorials/beginner/blitz/tensor\_tutorial.html}}
and Tensorflow\footnote{\url{https://www.tensorflow.org/tutorials/customization/basics}}
provide tensor APIs with NumPy-inspired semantics.
It is also implemented in packages that support sparse arrays
such as \code{scipy.sparse} and \code{pydata.sparse}.
Another notable example is Dask, a library for parallel computing in
Python.  Dask adopts the NumPy API and therefore presents a familiar
interface to existing NumPy users, while adding powerful abilities to
parallelize and distribute tasks.

>>>>

NumPy plays a central role in building and standardizing much of the scientific
Python community infrastructure.
NumPy's docstring standard is now widely adopted.
We are also now using the NEP system as a way to help coordinate the larger
scientific Python community.
% https://numpy.org/neps/nep-0029-deprecation_policy.html
For example, in NEP 29, we recommend, along with leaders from various other
projects, that all projects across the Scientific Python ecosystem adopt a
common ``time window-based'' policy for support of Python and NumPy versions.
This standard will simplify downstream project and release planning.

@@

A vast number of projects are built on NumPy;
these projects are consumers of the NumPy API.
Over the last several years, a growing number of projects are providers of
a \emph{NumPy-like API} and array objects targeting audiences with specialized
needs beyond NumPy's capabilities.
For example, the NumPy API is implemented by several popular tensor computation
libraries including CuPy\footnote{\url{https://cupy.chainer.org/}},
JAX\footnote{\url{https://jax.readthedocs.io/en/latest/jax.numpy.html}},
and Apache MXNet\footnote{\url{https://numpy.mxnet.io/}}.
PyTorch\footnote{\url{https://pytorch.org/tutorials/beginner/blitz/tensor\_tutorial.html}}
and Tensorflow\footnote{\url{https://www.tensorflow.org/tutorials/customization/basics}}
provide tensor APIs with NumPy-inspired semantics.
It is also implemented in packages that support sparse arrays
such as \code{scipy.sparse} and PyData/Sparse.
Another notable example is Dask, a library for parallel computing in
Python.  Dask adopts the NumPy API and therefore presents a familiar
interface to existing NumPy users, while adding powerful abilities to
parallelize and distribute tasks.
